---
title: "Explanation of SNspread package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explanation of SNspread package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Overview
- Functionality
- Basic usage
- Shiny interface

### Functionality
The ```SNspread``` package gives you the ability to create a network of friends
(```create_network```), update their gender and names (```update_network```), and
visualize the network with ```create_graph```. Moreover, the spread of disease 
within the network can be simulated using the ```sim_spread``` function. Code to use
the package as a shiny app is also provided.

### Basic usage
Example of how to use the package.

```{r basic}
library(SNspread)
library(qgraph)
network1 <- create_network(n = 25)
network1v1 <- update_network(network1, names = c("Jan", "Piet", "Else", "Sarah"))
network1v2 <- sim_spread(network1v1, spread_rate = 5)
network1v3 <- sim_spread(network1v2, spread_rate = 5)
create_graph(network1) # Initial network
create_graph(network1v1) # Updated network
create_graph(network1v2) # Spread starts with user
create_graph(network1v3) # Simulate spread through network
```

Note that you can also change the gender of friends, using the ```update_graph``` 
function. For example:

```{r extra}
size <- 15
network2 <- create_network(n = size)
network2v1 <- update_network(network2, gender = sample(c(1, 2), (size + 1), replace = TRUE))
create_graph(network2v1)
```


### Shiny interface
Besides the basic usage of the package, the package can also be ran as a ShinyApp.
The server.R and ui.R are provided in the package. This gives you the possibility to
update the network per node, and to simulate the spread of a disease several times.
